Make any stupid plot you want

### 2020-12-21 draft/sections/math.tex
what even is xi?

\begin{equation}
\mathcal{T}_b = \{U\subseteqq B: \{p \in E: [p] \in U\}\in \mathcal{T}_E\}
\end{equation}

@@

\subsubsection{Fiber}
Every point in the base space $b \in B$ has a local open set neighborhood $U$ \cite{FiberBundle2020, rowlandFiberBundle}

@@

\subsubsection{Fiber Space $F$}
We use Spivak's formalization of data base schemas as the basis of our fiber space $F$ \cite{spivakSIMPLICIALDATABASES}. He defines the type specification 
\begin{equation}
\pi: U \rightarrow DT
\end{equation}

@@

The artist is a mapping from the sheaf $O(E)$ representing the data to a pre-render space $O(H)$. 
\begin{equation}
    A: O(E) \rightarrow O(H)
\end{equation}
The artist is composed of two stages, data $E$ to visual mappings $V$ and $V$ mappings composited to a visual in prerender space $H$:
\begin{equation}
insert triangle here
\end{equation}

The first stage of the artist $F: E \rightarrow V$ maps from data space to visual variable  \cite{carpendaleVisualRepresentationSemiology,bertinIIPropertiesGraphic2011,munznerWhatDataAbstraction2014} space
%%include the $
\begin{equation}
    \begin{tikzcd}
        E \arrow[d, "\pi"'] \arrow[r, "\nu"]                                        & V \arrow[ld, "\pi"'] \\
        K \arrow[u, "\tau"', bend right] \arrow[ru, "\mu"', bend right, shift left] &                     
        \end{tikzcd}
\end{equation}

such that $\nu: \tau \mapsto \mu$ is a homorphism where $\tau$ and $\mu$ are equivariant such that the properties of the field type persist in the visual representation. The map $\xi: S \rightarrow K$ goes from a region $s$ to it associated $k$
\begin{equation}
    \begin{tikzcd}
        E \arrow[d, "\pi"'] & H \arrow[d, "\pi"'] \\
        K                   & S \arrow[l, "\xi"']
        \end{tikzcd}
\end{equation}
such that when $\xi(s) = k$, there is a mapping from screen space to k  $\xi^*\tau(s) = \tau(k)$. The visual fiber bundle $V$ gets pulled back over $S$ via $\xi$ such that 
\begin{equation}
    \begin{tikzcd}
        \xi^*V \arrow[r, "q"']                      & H \\
        S \arrow[u, "\xi^*\mu"] \arrow[ru, "\rho"'] &  
        \end{tikzcd}
\end{equation}
the composition $q \circ \xi^*\mu$ generates the $\rho$ function described in section~\ref{sec:display}.

An artist is the choice of ..... constraints are maps that preserve
\subsubsection{Compositing}

@@

\subsubsection{Channels}
Each $\nu$ function maps a field $\tau_c$ to a paramterized visual field $\mu$, for example the color or shape visual channels \cite{bertinIIPropertiesGraphic2011,munznerMarksChannels}. The set of $\nu$ is a functor from data to visual space such that any $\nu$ is an equivariant map if

>>>>

\begin{equation}
    \label{eq:base_space}
\mathcal{T}_b = \{U\subseteqq B: \{p \in E: [p] \in U\}\in \mathcal{T}_E\}
\end{equation}

@@

\subsubsection{Fiber}
As shown in equation!\ref{eg:base_space}, every point $b \in B$ has a local open set neighborhood $U$ \cite{FiberBundle2020, rowlandFiberBundle}

@@

\subsubsection{Fiber Space $F$}
\label{sec:data_fiber}
We use Spivak's formalization of data base schemas as the basis of our fiber space $F$ \cite{spivakSIMPLICIALDATABASES}. He defines the type specification 
\begin{equation}
\pi: U \rightarrow DT
\end{equation}

@@

The artist is a mapping from the sheaf $O(E)$ representing the data to a pre-render space $O(H)$. 
\begin{equation}
    A: O(E) \rightarrow O(H)
\end{equation}
The artist is composed of two stages, data $E$ to visual mappings $V$ and $V$ mappings composited to a visual in prerender space $H$. The visual fiber bundle $V$ shares basespace $K$ with $E$:

\begin{equation}
    \begin{tikzcd}
        P \arrow[r, hook] & V \arrow[r, "\pi"] & K\\   
    \end{tikzcd}
\end{equation}

with fiber $P$ that encodes visual paramters such as position or color. As in section~\ref{sec:data_fiber}, the fields in $P$ are strongly typed. The function $\nu: E \rightarrow V$ maps from data space to visual space  \cite{carpendaleVisualRepresentationSemiology,bertinIIPropertiesGraphic2011,munznerWhatDataAbstraction2014} space
\begin{equation}
    \begin{tikzcd}
        E \arrow[d, "\pi"'] \arrow[r, "\nu"] & V \arrow[ld, "\pi"'] \\
        K                                    &                     
        \end{tikzcd}
\end{equation}

such that the visual section $\mu: K \rightarrow V$ 
\begin{equation}
    \begin{tikzcd}
        E \arrow[r, "\nu"]                      & V \\
        K \arrow[ru, "\mu"'] \arrow[u, "\tau"'] &  
        \end{tikzcd}

\end{equation}

where visual transformers $\nu$ applied to data $\tau$ is equivalent to $\mu$ such that $\mu(k) = \nu\circ\tau(k)$. To obtain the equivalent visual values in screen space $S$, the look up map $\xi: S \rightarrow K$ goes from a region $s$ to it associated $k$
\begin{equation}
    \begin{tikzcd}
        E \arrow[d, "\pi"'] & H \arrow[d, "\pi"'] \\
        K                   & S \arrow[l, "\xi"']
        \end{tikzcd}
\end{equation}
such that when $\xi(s) = k$, there is a mapping from screen space to k  $\xi^*\tau(s) = \tau(k)$. The visual fiber bundle $V$ gets pulled back over $S$ via $\xi$ such that 
\begin{equation}
    \begin{tikzcd}
        \xi^*V \arrow[r, "Q"] \arrow[rd, "\xi^*\pi"'] & H \arrow[d, "\pi"] \\
                                                      & S                 
    \end{tikzcd}
\end{equation}
the function $Q:\xi^*V\rightarrow H$ composites points in $V$ into $\mathbb{R^7}$ tuples. The section $\mu$ is pulled over $s$

\begin{equation}
    \begin{tikzcd}
        \xi^*V \arrow[r, "Q"] & H                                           \\
                              & S \arrow[lu, "\xi^*\mu"] \arrow[u, "\rho"']
    \end{tikzcd}
\end{equation}

such that the composition $Q$ of $\mu$ is equivalent to the render $\rho(s) = Q\circ\mu(s)$. The full visualization path is
\begin{equation} 
    \begin{tikzcd}
        E \arrow[r, "\nu=transforms"] & V                                                              & \xi^*V \arrow[r, "Q = \text{set attrs}"]                             & H \\
                                  & K \arrow[lu, "\tau = data"] \arrow[u, "{\mu = \{\tau,\nu\}}"'] & S \arrow[l, "\xi - init?draw"] \arrow[u, "\xi^*\mu = \nu\circ\tau"'] &  
    \end{tikzcd}
\end{equation}

\subsubsection{Compositing}

@@

\subsubsection{Channels}

%% the \mu [oeve gpes here maybe]
Each $\nu$ function maps a field $\tau_c$ to a paramterized visual field $\mu$, for example the color or shape visual channels \cite{bertinIIPropertiesGraphic2011,munznerMarksChannels}. The set of $\nu$ is a functor from data to visual space such that any $\nu$ is an equivariant map if
